Human Factors Influencing Visual Statistical Inference

### 2014-01-09 sociology_paper.tex
figure 4 demographic_effect.pdf updated

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=4in]{demographic_effect.pdf} 
   \caption{Boxplots of average log time taken and proportion correct responses of all the lineups plotted for each demographic factor levels. The dots inside the boxes represent means. Some differences in means of various demographic factors are observed. Variability in proportion correct indicates large variability in lineup difficulties. \dc{*** Vertical axis needs to be labelled ``detection rate'' for bottom row, and ``value'' needs to be removed.}}
   \label{fig:demographic_effect}
\end{figure}

>>>>

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=4in]{demographic_effect.pdf} 
   \caption{Boxplots of average log time taken and proportion correct responses (detection rate) of all the lineups plotted for each demographic factor levels. The dots inside the boxes represent means. Some differences in means of various demographic factors are observed. Variability in detection rate indicates large variability in lineup difficulties. }
   \label{fig:demographic_effect}
\end{figure}

%\dc{*** Vertical axis needs to be labelled ``detection rate'' for bottom row, and ``value'' needs to be removed.}
